The evolution of gene expression in the term placenta of viviparous mammals

### 2016-08-12 manuscript/manuscript.Rnw
remove top50 tables

\begin{table}
  \footnotesize
<<top.50.human.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="homo sapiens"))
@ 
\caption{The top 50 genes by \ac{FPKM} in \human which are not
  annotated as Mt\_rRNA, Mt\_tRNA, rRNA or a housekeeping gene. Gene
  symbol is the gene symbol or Ensembl gene id. Human Name is the HUGO
  name corresponding to the human symbol. A complete list of all genes
  is in \cref{tab:all_homo_sapiens_placenta}.}
\label{tab:top50_human_placenta}
\end{table}

@@

\begin{table}
  \footnotesize
<<top.50.bonobo.expressed.genes,echo=FALSE,results="asis">>=
top.bonobo.genes <- top.genes.table(species.name="pan paniscus")
output.top.genes.table(top.bonobo.genes)
setkey(top.bonobo.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\bonobo}{tab:all_pan_paniscus_placenta}}
\label{tab:top50_bonobo_placenta}
\end{table}

@@

\begin{table}[h]
  \footnotesize
<<top.50.mouse.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="mus musculus"))
@ 
\caption{\tableexplanation{\mouse}{tab:all_mus_musculus_placenta}}
\label{tab:top50_mouse_placenta}
\end{table}

@@

\begin{table}[h]
  \footnotesize
<<top.50.n.galili.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="spalax galili"))
@ 
\caption{\tableexplanation{\galili}{tab:all_spalax_galili_placenta}}
\label{tab:top50_n_galili_placenta}
\end{table}

@@

\begin{table}[h]
  \footnotesize
<<top.50.s.carmeli.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="spalax carmeli"))
@ 
\caption{\tableexplanation{\carmeli}{tab:all_spalax_carmeli_placenta}}
\label{tab:top50_s_carmeli_placenta}
\end{table}

@@

\begin{table}
  \footnotesize
<<top.50.dog.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="canis familiaris"))
@ 
\caption{\tableexplanation{\dog}{tab:all_canis_familiaris_placenta}}
\label{tab:top50_dog_placenta}
\end{table}

@@

\begin{table}
  \footnotesize
<<top.50.cow.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="bos taurus"))
@ 
\caption{\tableexplanation{\cow}{tab:all_bos_taurus_placenta}}
\label{tab:top50_cow_placenta}
\end{table}

@@

\begin{table}[h]
  \footnotesize
<<top.50.pig.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="sus scrofa"))
@ 
\caption{\tableexplanation{\pig}{tab:all_sus_scrofa_placenta}}
\label{tab:top50_pig_placenta}
\end{table}

@@

\begin{table}[h]
  \footnotesize
<<top.50.horse.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="equus caballus"))
@ 
\caption{\tableexplanation{\horse}{tab:all_equus_caballus_placenta}}
\label{tab:top50_horse_placenta}
\end{table}

@@

\begin{table}[h]
  \footnotesize
<<top.50.sheep.expressed.genes,echo=FALSE,results="asis">>=
top.sheep.genes <- top.genes.table(species.name="ovis aries",n=200)
top.sheep.genes <-
    top.sheep.genes[!grepl("\\{(7SK|.+_([SM]RP|nuc)|SNOR[AD]\\d+|U\\d+|HIST.*)\\}",
                           `Gene symbol`) &
                    !grepl("\\((7SK|.+_([SM]RP|nuc)|SNOR[AD]\\d+|U\\d+|HIST.*)\\)",
                           `Human Symbol`)
                   ,][1:50,]
output.top.genes.table(top.sheep.genes)
@ 
\caption{\tableexplanation{\sheep}{tab:all_ovis_aries_placenta}}
\label{tab:top50_sheep_placenta}
\end{table}

@@

\begin{table}
\footnotesize
<<top.50.elephant.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="loxodonta africana"))
@ 
\caption{\tableexplanation{\elephant}{tab:top50_elephant_placenta}}
\label{tab:top50_elephant_placenta}
\end{table}

@@

\begin{table}
\footnotesize
<<top.50.armadillo.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="dasypus novemcinctus"))
@ 
\caption{\tableexplanation{\armadillo}{tab:all_dasypus_novemcinctus_placenta}}
\label{tab:top50_armadillo_placenta}
\end{table}

@@

\begin{table}
  \footnotesize
<<top.50.opossum.expressed.genes,echo=FALSE,results="asis">>=
output.top.genes.table(top.genes.table(species.name="monodelphis domestica"))
@ 
\caption{\tableexplanation{\opossum}{tab:all_monodelphis_domestica_placenta}}
\label{tab:top50_opossum_placenta}
\end{table}

@@

  \printaddresses

\end{backmatter}

>>>>

% \begin{table}
%   \footnotesize
% <<top.50.human.expressed.genes,echo=FALSE,results="asis">>=
% output.top.genes.table(top.genes.table(species.name="homo sapiens"))
% @ 
% \caption{The top 50 genes by \ac{FPKM} in \human which are not
%   annotated as Mt\_rRNA, Mt\_tRNA, rRNA or a housekeeping gene. Gene
%   symbol is the gene symbol or Ensembl gene id. Human Name is the HUGO
%   name corresponding to the human symbol. A complete list of all genes
%   is in \cref{tab:all_homo_sapiens_placenta}.}
% \label{tab:top50_human_placenta}
% \end{table}

@@

% \begin{table}
%   \footnotesize
% <<top.50.bonobo.expressed.genes,echo=FALSE,results="asis">>=
% top.bonobo.genes <- top.genes.table(species.name="pan paniscus")
% output.top.genes.table(top.bonobo.genes)
% setkey(top.bonobo.genes,"Gene symbol")
% @ 
% \caption{\tableexplanation{\bonobo}{tab:all_pan_paniscus_placenta}}
% \label{tab:top50_bonobo_placenta}
% \end{table}

@@

% \begin{table}[h]
%   \footnotesize
% <<top.50.mouse.expressed.genes,echo=FALSE,results="asis">>=
% output.top.genes.table(top.genes.table(species.name="mus musculus"))
% @ 
% \caption{\tableexplanation{\mouse}{tab:all_mus_musculus_placenta}}
% \label{tab:top50_mouse_placenta}
% \end{table}

@@

% \begin{table}[h]
%   \footnotesize
% <<top.50.n.galili.expressed.genes,echo=FALSE,results="asis">>=
% output.top.genes.table(top.genes.table(species.name="spalax galili"))
% @ 
% \caption{\tableexplanation{\galili}{tab:all_spalax_galili_placenta}}
% \label{tab:top50_n_galili_placenta}
% \end{table}

@@

% \begin{table}[h]
%   \footnotesize
% <<top.50.s.carmeli.expressed.genes,echo=FALSE,results="asis">>=
% output.top.genes.table(top.genes.table(species.name="spalax carmeli"))
% @ 
% \caption{\tableexplanation{\carmeli}{tab:all_spalax_carmeli_placenta}}
% \label{tab:top50_s_carmeli_placenta}
% \end{table}

@@

% \begin{table}
%   \footnotesize
% <<top.50.dog.expressed.genes,echo=FALSE,results="asis">>=
% output.top.genes.table(top.genes.table(species.name="canis familiaris"))
% @ 
% \caption{\tableexplanation{\dog}{tab:all_canis_familiaris_placenta}}
% \label{tab:top50_dog_placenta}
% \end{table}

@@

% \begin{table}
%   \footnotesize
% <<top.50.cow.expressed.genes,echo=FALSE,results="asis">>=
% output.top.genes.table(top.genes.table(species.name="bos taurus"))
% @ 
% \caption{\tableexplanation{\cow}{tab:all_bos_taurus_placenta}}
% \label{tab:top50_cow_placenta}
% \end{table}

@@

% \begin{table}[h]
%   \footnotesize
% <<top.50.pig.expressed.genes,echo=FALSE,results="asis">>=
% output.top.genes.table(top.genes.table(species.name="sus scrofa"))
% @ 
% \caption{\tableexplanation{\pig}{tab:all_sus_scrofa_placenta}}
% \label{tab:top50_pig_placenta}
% \end{table}

@@

% \begin{table}[h]
%   \footnotesize
% <<top.50.horse.expressed.genes,echo=FALSE,results="asis">>=
% output.top.genes.table(top.genes.table(species.name="equus caballus"))
% @ 
% \caption{\tableexplanation{\horse}{tab:all_equus_caballus_placenta}}
% \label{tab:top50_horse_placenta}
% \end{table}

@@

% \begin{table}[h]
%   \footnotesize
% <<top.50.sheep.expressed.genes,echo=FALSE,results="asis">>=
% top.sheep.genes <- top.genes.table(species.name="ovis aries",n=200)
% top.sheep.genes <-
%     top.sheep.genes[!grepl("\\{(7SK|.+_([SM]RP|nuc)|SNOR[AD]\\d+|U\\d+|HIST.*)\\}",
%                            `Gene symbol`) &
%                     !grepl("\\((7SK|.+_([SM]RP|nuc)|SNOR[AD]\\d+|U\\d+|HIST.*)\\)",
%                            `Human Symbol`)
%                    ,][1:50,]
% output.top.genes.table(top.sheep.genes)
% @ 
% \caption{\tableexplanation{\sheep}{tab:all_ovis_aries_placenta}}
% \label{tab:top50_sheep_placenta}
% \end{table}

@@

% \begin{table}
% \footnotesize
% <<top.50.elephant.expressed.genes,echo=FALSE,results="asis">>=
% output.top.genes.table(top.genes.table(species.name="loxodonta africana"))
% @ 
% \caption{\tableexplanation{\elephant}{tab:top50_elephant_placenta}}
% \label{tab:top50_elephant_placenta}
% \end{table}

@@

% \begin{table}
% \footnotesize
% <<top.50.armadillo.expressed.genes,echo=FALSE,results="asis">>=
% output.top.genes.table(top.genes.table(species.name="dasypus novemcinctus"))
% @ 
% \caption{\tableexplanation{\armadillo}{tab:all_dasypus_novemcinctus_placenta}}
% \label{tab:top50_armadillo_placenta}
% \end{table}

@@

% \begin{table}
%   \footnotesize
% <<top.50.opossum.expressed.genes,echo=FALSE,results="asis">>=
% output.top.genes.table(top.genes.table(species.name="monodelphis domestica"))
% @ 
% \caption{\tableexplanation{\opossum}{tab:all_monodelphis_domestica_placenta}}
% \label{tab:top50_opossum_placenta}
% \end{table}

@@

%  \printaddresses

%\end{backmatter}
